### 2023-12-02 chapters/paper_benchmarking_workshop.tex
Update footnote placement

\paragraph{Scope and related work} 
At a high level, this benchmark brings order to LVM model comparisons for speech and also provides useful reference implementations of the models\footnote{\texttt{ \href{https://github.com/JakobHavtorn/benchmarking-lvms}{github.com/JakobHavtorn/benchmarking-lvms}}}. 
An extended version of this paper is available at \href{https://arxiv.org/abs/2202.12707}{arXiv:2202.12707}.
LVMs based on the VAE are of interest due to their ability to learn an approximate posterior distribution over latent variables. This makes them useful beyond generation for e.g. semi"=supervised learning \parencite{kingma_semi-supervised_2014} and anomaly detection \parencite{havtorn_hierarchical_2021}. 
In this paper, we focus on the VRNN \parencite{chung_recurrent_2015}, SRNN \parencite{fraccaro_sequential_2016} and STCN \parencite{aksan_stcn_2019} since they are similar to the original VAE framework. 
We exclude some related work from the benchmark. Specifically, the FH-VAE \parencite{hsu_unsupervised_2017} adds a global latent variable but we exclude it due to it's segmentation of the training data. We also exclude Z-forcing \parencite{goyal_zforcing_2017} which resembles the SRNN, but deviates from maximum likelihood training by using an auxiliary loss. We exclude the VQ-VAE \parencite{oord_neural_2018} which is a hybrid LVM and autoregressive model, since it uses a quantized latent space. Finally, we exclude the Stochastic WaveNet \parencite{lai_stochastic_2018} which is similar, but inferior, to the STCN \parencite{aksan_stcn_2019}.

>>>>

\paragraph{Scope and related work} 
At a high level, this benchmark brings order to LVM model comparisons for speech and also provides useful reference implementations of the models.\footnote{\texttt{ \href{https://github.com/JakobHavtorn/benchmarking-lvms}{github.com/JakobHavtorn/benchmarking-lvms}}} 
An extended version of this paper is available at \href{https://arxiv.org/abs/2202.12707}{arXiv:2202.12707}.
LVMs based on the VAE are of interest due to their ability to learn an approximate posterior distribution over latent variables. This makes them useful beyond generation for e.g. semi"=supervised learning \parencite{kingma_semi-supervised_2014} and anomaly detection \parencite{havtorn_hierarchical_2021}. 
In this paper, we focus on the VRNN \parencite{chung_recurrent_2015}, SRNN \parencite{fraccaro_sequential_2016} and STCN \parencite{aksan_stcn_2019} since they are similar to the original VAE framework. 
We exclude some related work from the benchmark. Specifically, the FH-VAE \parencite{hsu_unsupervised_2017} adds a global latent variable but we exclude it due to it's segmentation of the training data. We also exclude Z-forcing \parencite{goyal_zforcing_2017} which resembles the SRNN, but deviates from maximum likelihood training by using an auxiliary loss. We exclude the VQ-VAE \parencite{oord_neural_2018} which is a hybrid LVM and autoregressive model, since it uses a quantized latent space. Finally, we exclude the Stochastic WaveNet \parencite{lai_stochastic_2018} which is similar, but inferior, to the STCN \parencite{aksan_stcn_2019}.

### 2023-12-02 chapters/paper_brief.tex
Change references and add todos
Add source reference at the top of every paper chapter
Fix references
Add citation to top reference
Update initial reference
Update top reference
Add label
Update footnote placement

\chapter[a brief overview of unsupervised neural speech representation learning]{A Brief Overview of Unsupervised Neural Speech Representation Learning}
\label{app:paper-brief}
\ifthenelse{\equal{\skipappendices}{true}}{}{

@@

In brief, LVMs of the VAE-type consist of an approximate posterior, $q(\mathbf{z}|\mathbf{x})$, an observation model, $p(\mathbf{x}|\mathbf{z})$, and a prior, $p(\mathbf{z})$. 
With reference to probabilistic coding theory, the approximate posterior is often referred to as the encoder and the observation model as the decoder \parencite{kingma_autoencoding_2014, rezende_stochastic_2014}. From a theoretical perspective, the encoder exists solely as the result of choosing to use variational inference to train the decoder rather than e.g. MCMC. As such, it is also referred to as the inference model. However, from a representation learning perspective, the encoder is essential as it can be used to efficiently obtain the representation $\mathbf{z}$ commonly used for downstream tasks. 
It is still possible to evaluate and sample the true posterior distribution $p(\mathbf{z}|\mathbf{x})$ by applying MCMC methods such as Hamiltonian Monte Carlo on the decoder, but for computational reasons this is rarely done in practice.

@@

\section{Discussion}
\label{sec:mtax}

>>>>

\chapter[a brief overview of unsupervised neural speech representation learning]{A Brief Overview of Unsupervised Neural Speech Representation Learning}
\label{chp:paper-brief}

\textit{This chapter is a piece of original research published as part of the project:} \newline
\begin{center}
    \begin{enumerate}[leftmargin=8mm,rightmargin=8mm,topsep=0mm,label={[\Alph*]}]
        \setcounter{enumi}{2}
        \item \fullcite{borgholt_brief_2022} \co \hspace{0.1em} \parencite{borgholt_brief_2022}
        \end{enumerate}
\end{center}

\ifthenelse{\equal{\skipappendices}{true}}{}{

@@

In brief, LVMs of the VAE type consist of an approximate posterior, $q(\mathbf{z}|\mathbf{x})$, an observation model, $p(\mathbf{x}|\mathbf{z})$, and a prior, $p(\mathbf{z})$. 
With reference to probabilistic coding theory, the approximate posterior is often referred to as the encoder and the observation model as the decoder \parencite{kingma_autoencoding_2014, rezende_stochastic_2014}. From a theoretical perspective, the encoder exists solely as the result of choosing to use variational inference to train the decoder rather than e.g. MCMC. As such, it is also referred to as the inference model. However, from a representation learning perspective, the encoder is essential as it can be used to efficiently obtain the representation $\mathbf{z}$ commonly used for downstream tasks. 
It is still possible to evaluate and sample the true posterior distribution $p(\mathbf{z}|\mathbf{x})$ by applying MCMC methods such as Hamiltonian Monte Carlo on the decoder, but for computational reasons this is rarely done in practice.

@@

\section{Discussion}
\label{paper_brief_sec: discussion}

### 2023-12-02 chapters/paper_retrospective.tex
Minor formatting
Update footnote placement

From the CAD medical records, we included all calls that could be matched to a corresponding audio file for 1-1-2 and MH-1813 from 2015 to 2021 for patients older than 18. The CAD records were matched with the telephone call recordings based on the call start, call duration, and call-taker identity. Due to data incompleteness, and the way the audio data is stored, at CEMS, 2,730,199 contacts could not be matched to their corresponding audio file, however, 2,361,178 contacts were successfully matched. We found no obvious pattern in the matched and unmatched calls and we included all calls with at matching audio file. Next, a call was regarded as a case of ground truth stroke positive when the CPR number in the CAD record matched that of a DanStroke record, and the patient-reported time of onset was close to the call start time. We allowed a window of 72 hours before and 24 hours after the call starts to account for uncertainty in recording stroke onset time. We excluded calls involving subarachnoid hemorrhage cases. Finally, we considered a call to be a call-taker stroke positive when the call-taker selected the stroke diagnostic category during the call and dispatched an ambulance with the appropriate level of response \parencite{cite20}. To ensure that the effect of the machine learning framework was not overestimated, we excluded calls where diagnostic category had not been registered from the test set. We still reported the population characteristics and model performance of this group of calls to assess potential bias introduced by excluding them. A data-flow diagram is included in \cref{app:supplementary-retrospective}. The resulting dataset is the largest dataset of audio files from stroke calls collected to date.

@@

The datasets used to evaluate call-taker performance and to train and evaluate the machine learning framework are legally restricted by Danish patient privacy and secrecy laws and are therefore, not publicly available. The data can be made available from the publication date but requires a Data Access Agreement, which is examined and approved by the ethics committees that approved this research \footnote{Danish Data Protection Agency, \url{https://www.datatilsynet.dk/english}}. For the same reason, the machine learning framework trained in this study is not publicly available; however, instructions on how to train it are included in the main manuscript and the supplementary material.

>>>>

From the CAD medical records, we included all calls that could be matched to a corresponding audio file for 1-1-2 and MH-1813 from 2015 to 2021 for patients older than 18. The CAD records were matched with the telephone call recordings based on the call start, call duration, and call-taker identity. Due to data incompleteness, and the way the audio data is stored, at CEMS, 2,730,199 contacts could not be matched to their corresponding audio file, however, 2,361,178 contacts were successfully matched. We found no obvious pattern in the matched and unmatched calls, and we included all calls with at matching audio file. Next, a call was regarded as a case of ground truth stroke positive when the CPR number in the CAD record matched that of a DanStroke record, and the patient-reported time of onset was close to the call start time. We allowed a window of 72 hours before and 24 hours after the call starts to account for uncertainty in recording stroke onset time. We excluded calls involving subarachnoid hemorrhage cases. Finally, we considered a call to be a call-taker stroke positive when the call-taker selected the stroke diagnostic category during the call and dispatched an ambulance with the appropriate level of response \parencite{cite20}. To ensure that the effect of the machine learning framework was not overestimated, we excluded calls where diagnostic category had not been registered from the test set. We still reported the population characteristics and model performance of this group of calls to assess potential bias introduced by excluding them. A data-flow diagram is included in \cref{app:supplementary-retrospective}. The resulting dataset is the largest dataset of audio files from stroke calls collected to date.

@@

The datasets used to evaluate call-taker performance and to train and evaluate the machine learning framework are legally restricted by Danish patient privacy and secrecy laws and are therefore, not publicly available. The data can be made available from the publication date but requires a Data Access Agreement, which is examined and approved by the ethics committees that approved this research.\footnote{Danish Data Protection Agency, \url{https://www.datatilsynet.dk/english}} For the same reason, the machine learning framework trained in this study is not publicly available; however, instructions on how to train it are included in the main manuscript and the supplementary material.
